
\documentclass[letterpaper,10pt]{article}
\usepackage[margin=0.8in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\begin{document}
\section*{Humanized Resume Summary}
\begin{itemize}[leftmargin=0.3in]
\item \#1
\item Conceptualized and executed a DeBERTa-based architecture enhanced with emotion embeddings and word attention mechanisms using Bi-LSTM for implicit hate speech detection tasks resulting in a 5\\% gain over baseline models in F1-score.
\item Utilized supervised contrastive learning to enhance the representation of features, leading to an 8 \\% improvement in classification accuracy using the IHSate and IHC datasets.
\item Constructed emotion synthesis pipelines that incorporated sentiment features using the NRC Lexicon, which led to a 6\\% improvement in model accuracy.
\item Created and implemented MaxViT based models for histopathological image classification with a classifying accuracy of 92\\% on large-scale medical datasets.
\item Developed Engineered a Cascaded Deformable Transformer Layers (CDTL) approach to improve dependency modeling by 20\\%, facilitating AI workflows in medical imaging.
\item Applied Cascaded Deformable Self-Attention (CDSA) method to increase per-category feature extraction performance by 18\\% across 10,000+ annotated medical images.
\item Created and implemented models based on the MaxViT structure for the classification of histopathological images, achieving a classification accuracy of 92\\% in the large scale medical database.
\item Engineered Cascaded Deformable Transformer Layers (CDTL) to improve feature dependency modeling by 20\\%, optimizing AI workflows in medical imaging.
\item Implemented Cascaded Deformable Self-Attention (CDSA) to increase category-specific feature extraction by 18\\% on 10,000+ annotated medical images.
\item Shipped \textbackslash textbf\VISDOM – Pixels to Reports
\item Designed a multi-stage pipeline: \textbackslash textbf\YOLOv8
\item Built dual OCR pathways: \textbackslash textbf\YOLO-OCR
\end{itemize}
\end{document}
